MSGARCH

### 2019-01-13 ms-garch.Rmd
增加了注释

```{r}
library(zoo)
library(forecast)
library(tseries)
library(xts)
library(ggplot2)
library(FinTS)
library(moments)
library(devtools)
library(FinTS)
library(MSGARCH)#当中GARCH的阶数如何选择
rm(list=ls())
#上海银行同业拆借率
data=read.csv("F:\\shibor分析\\shibor原始数据\\shibor_data.csv",header=T)
shibor<-data[,2]
par(mfrow=c(1,2))
shibor.date<-as.Date(data[,1])
plot(shibor.date,shibor,type="l",xlab="日期",ylab="隔夜拆借利率")

>>>>

```{r}
## 准备
options(digtis=4)
graphics.off()
rm(list=ls())

## 加载包
library(zoo)
library(forecast)
library(tseries)
library(xts)
library(ggplot2)
library(FinTS)
library(moments)
library(devtools)
library(FinTS)
library(MSGARCH)#当中GARCH的阶数如何选择

## 载入数据
#上海银行同业拆借率
data=read.csv("F:\\shibor分析\\shibor原始数据\\shibor_data.csv",header=T)
shibor<-data[,2]
par(mfrow=c(1,2))
shibor.date<-as.Date(data[,1])
plot(shibor.date,shibor,type="l",xlab="日期",ylab="隔夜拆借利率")
